SPAMDA: A software tool to manage meteorological data for environmental modelling

### 2020-02-27 latex_manuscript/elsevier/5_Advances_in_Engineering_Software/spamda.tex
Sending to Advances in Engineering Software journal. Latex and letters files.

\journal{Energy Conversion and Management}

@@

		A better understanding of the environment is of vital importance for science, contributing not only to more efficient exploitation of natural resources but also to the development of new strategies aimed at its protection. In that sense, meteorological observations provide an essential and valuable source of information which is widely used by researchers to address environmental learning, comprehension, prediction and conservation in numerous oceanic and atmospheric studies of a wide variety of areas (e.g. energy, climate change, agriculture, etc.). Some specific examples of the diversity of fields in which meteorological data can be used in are, among others: photovoltaic power forecasting \cite{WANG2019443}, directional analysis of sea storms \cite{LAFACE201545}, wind power ramp events prediction \cite{DORADOMORENO2017428}, offshore wind and wave exploitation \cite{WEISS201843}, impact of atmospheric components on clear-sky solar irradiance estimation \cite{ANTONANZASTORRES2016122}, study of the responses exhibited by plankton to fluid motions \cite{FUCHS2016109}, trends in solar radiation \cite{SILVA20101852} or simulation of extreme near shore sea conditions \cite{GOULDBY201415}. All these studies require a prior data collection and its adaptation to a specific format that allows the interpretation of them.

		On the other hand, special purpose software is usually developed to help researchers to advance in their studies related to energy and environmental modelling, becoming a great support for decision-making in the exploitation and protection of the environment. In \cite{CAMARGONOGUEIRA2016361}, a software tool for designing solar water heating systems is developed, which simulates different situations and finds the best technical and economical solution. In \cite{LO2015293}, an integrated simulation tool for the optimum design of bifacial solar panel with reflectors is presented. This tool can also be used to analyse the performance of the solar cells. A framework for data integration of offshore wind farms is implemented in \cite{NGUYEN2013150} in order to facilitate data exchange and improve operation and maintenance practices. In \cite{LIU2018516}, a software package to evaluate the performance of floating renewable energy systems is presented. A new wind turbine emulator for analysing the tower shadow and yaw error effects is developed in \cite{MOHAMMADI2018378}. Raabe et al. \cite{RAABE2010213} developed two software tools, \textit{Model of Equilibrium of Bay Beaches} (MEPBAY) and \textit{Coastal Modeling System} (SMC), to support different operational levels of headland-bay beach in coastal engineering projects, and a predictive tool to assess the energy performance in agrifood industries is developed in \cite{NUNES2014758}.

@@

		Currently, and as a support to traditional study procedures, Machine Learning (ML) techniques \cite{Alpaydin:2004:IML:1036287,Bishop:2006:PRM:1162264} are being widely used in numerous research fields related to classification, regression and optimisation tasks, obtaining significant improvements in the performance of the results \cite{TU20102938, WANG2019111799}. ML methodologies can be used not only by experienced computer scientists but also by other researchers. For example, the well-known \textit{Waikato Environment for Knowledge Analysis} (WEKA) \cite{WEKA} software tool provides researchers with a wide collection of ML algorithms. In this way, ML techniques have been already applied to tackle wave characterisation, accurately estimating $H_{s}$ and $T_{e}$ parameters \cite{DURANROSAL2017268, KUMAR2017605}, given that robustness of ML methods can tackle the previously explained difficulties in wave energy prediction. The problem is that, in order to apply these methods, it is essential to obtain datasets with relevant information about the issue under study, used to infer knowledge. Usually, these datasets are not publicly available in a friendly format, and their generation is the first step needed.

>>>>

\journal{Advances in Engineering Software}

@@

		A better understanding of the environment is of vital importance for science, contributing not only to more efficient exploitation of natural resources but also to the development of new strategies aimed at its protection. In that sense, meteorological observations provide an essential and valuable source of information which is widely used by researchers to address environmental learning, comprehension, prediction and conservation in numerous oceanic and atmospheric studies of a wide variety of areas (e.g. energy, climate change, agriculture, etc.). Some specific examples of the diversity of fields in which meteorological data can be used in are, among others: optimum layout design of onshore wind farms \cite{KALLIORAS20158}, directional analysis of sea storms \cite{LAFACE201545}, risk assessment of port areas exposed to intense wind actions \cite{REPETTO201829}, wind power ramp events prediction \cite{DORADOMORENO2017428}, structural health monitoring of dams \cite{KANG201960}, study of the responses exhibited by plankton to fluid motions \cite{FUCHS2016109}, trends in solar radiation \cite{SILVA20101852} or simulation of extreme near shore sea conditions \cite{GOULDBY201415}. All these studies require a prior data collection and its adaptation to a specific format that allows the interpretation of them.

		On the other hand, special purpose software is usually developed to help researchers to advance in their studies related to energy and environmental modelling, becoming a great support for decision-making in the exploitation and protection of the environment. In \cite{CAMARGONOGUEIRA2016361}, a software tool for designing solar water heating systems is developed, which simulates different situations and finds the best technical and economical solution. In \cite{LO2015293}, an integrated simulation tool for the optimum design of bifacial solar panel with reflectors is presented. This tool can also be used to analyse the performance of the solar cells. A framework for data integration of offshore wind farms is implemented in \cite{NGUYEN2013150} in order to facilitate data exchange and improve operation and maintenance practices. In \cite{KRATZIG201333}, a software tool to analysis solar updraft power plant design is presented. A review of software tools used for heating, ventilation, and air conditioning (HVAC) systems research, which are employed to study and reduce the energy consumption in buildings, is presented in \cite{OROSA2011846}. Raabe et al. \cite{RAABE2010213} developed two software tools, \textit{Model of Equilibrium of Bay Beaches} (MEPBAY) and \textit{Coastal Modeling System} (SMC), to support different operational levels of headland-bay beach in coastal engineering projects, and Su et al. \cite{SU20167} developed a large scale marine hydrological environmental data-oriented visualization software to simulate and show properties and change process of marine water environmental factors efficiently and intuitively.

@@

		Currently, and as a support to traditional study procedures, Machine Learning (ML) techniques \cite{Alpaydin:2004:IML:1036287,Bishop:2006:PRM:1162264} are being widely used in numerous research fields related to classification, regression and optimisation tasks, obtaining significant improvements in the performance of the results \cite{ZHOU20191,NOURANI2012127,GUO201816}. ML methodologies can be used not only by experienced computer scientists but also by other researchers. For example, the well-known \textit{Waikato Environment for Knowledge Analysis} (WEKA) \cite{WEKA} software tool provides researchers with a wide collection of ML algorithms. In this way, ML techniques have been already applied to tackle wave characterisation, accurately estimating $H_{s}$ and $T_{e}$ parameters \cite{DURANROSAL2017268, KUMAR2017605}, given that robustness of ML methods can tackle the previously explained difficulties in wave energy prediction. The problem is that, in order to apply these methods, it is essential to obtain datasets with relevant information about the issue under study, used to infer knowledge. Usually, these datasets are not publicly available in a friendly format, and their generation is the first step needed.
